% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Harold Hotelling}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://jblevins.org/projects/cv-template/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Naoya Muramatsu},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  \href{http://www.unc.edu/}{University of Tsukuba} \\
  Faculty of Library, Information and Media Science \\
  Graduate School of Library, Information and Media Studies
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & (080) 4465-4869 \\
    Email: & \href{mailto:sh.mn.nat@gmail.com}{\tt sh.mn.nat@gmail.com} \\
    Homepage: & \href{https://github.com/DenDen047/profile}{\tt https://github.com/DenDen047/profile} \\
  \end{tabular}
\end{minipage}


\section*{Personal}

\begin{itemize}
  \item Born on March 22, 1996.
  \item Japan Citizen.
\end{itemize}


\section*{Education}

\begin{itemize}
  \item pre-B.S. Enginner, National Institute of Technology, Nagano College, 2016.

  \item B.S. Library and information science, University of Tsukuba, 2018.

  \item M.A. Graduate School of Library, Information and Media Studies, University of Tsukuba, year 1.
\end{itemize}


\section*{Employment}

\begin{itemize}
  \item Pixie Dust Technologies, Inc. 2017--2018.
\end{itemize}


\section*{Publications}

% \subsection*{Journal Articles}

% \begin{itemize}
%   \item
% \end{itemize}

\subsection*{Proceedings}

\begin{itemize}
  \item Natsumi Kato*, Hiroyuki Osone*, Daitetsu Sato, {\bf Naoya Muramatsu}, and Yoichi Ochiai. 2018. DeepWear: a Case Study of Collaborative Design between Human and Artificial Intelligence. In {\it Proceedings of the Twelfth International Conference on Tangible, Embedded, and Embodied Interaction} (TEI ’18). ACM, New York, NY, USA, 529-536. DOI: \url{https://doi.org/10.1145/3173225.3173302} (* Joint first authorship.)

  \item Natsumi Kato, Hiroyuki Osone, Daitetsu Sato, {\bf Naoya Muramatsu}, and Yoichi Ochiai. 2017. Crowd Sourcing Clothes Design Directed by Adversarial Neural Networks. In {\it NIPS 2017 Workshop} (NIPS ’17). \url{https://nips2017creativity.github.io/}

  \item {\bf Naoya Muramatsu}, Chun Wei Ooi, Yuta Itoh, and Yoichi Ochiai. 2017. DeepHolo: recognizing 3D objects using a binary-weighted computer-generated hologram. In {\it SIGGRAPH Asia 2017 Posters} (SA ’17). ACM, New York, NY, USA, Article 29, 2 pages. DOI: \url{https://doi.org/10.1145/3145690.3145725}

  \item Mose Sakashita, Yuta Sato, Ayaka Ebisu, Keisuke Kawahara, Satoshi Hashizume, {\bf Naoya Muramatsu}, and Yoichi Ochiai. 2017. Haptic marionette: wrist control technology combined with electrical muscle stimulation and hanger reflex. In {\it SIGGRAPH Asia 2017 Posters} (SA ’17). ACM, New York, NY, USA, Article 33, 2 pages. DOI: \url{https://doi.org/10.1145/3145690.3145743}

  \item {\bf Naoya Muramatsu}, Kazuki Ohshima, Ryota Kawamura, Ooi Chun Wei, Yuta Sato, and Yoichi Ochiai. 2017. Sonoliards: Rendering Audible Sound Spots by Reflecting the Ultrasound Beams. In {\it UIST 2017 Demo} (UIST ’17). ACM, New York, NY, USA, 57-59. DOI: \url{https://doi.org/10.1145/3131785.3131807}

  \item {\bf Naoya Muramatsu}, Ooi Chun Wei, Takashi Miyazaki. 2017. Development of High Performance Filter for Indoor Positioning System. In {\it ICISIP 2017 Oral}.

  % \item 村松直哉, 佐藤哲司, 伏見卓恭. 2017. レビュー観点の推移パターンに基づく商品属性の抽出手法. In {\it DEIM 2017}. 学生プレゼンテーション賞.
\end{itemize}

\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}